Argennon: A Scalable Smart Contract Platform

### 2022-04-18 tex/sections/incentive.tex
Add the delegates reward
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

The Argennon protocol does not explicitly define any fees for normal transactions. Only for high priority
transactions a fixed fee is determined by the governance system (See Section ...). Because the protection of the
Argennon network against spams and DOS attacks is mostly done by the delegates, they are also responsible for
determining and collecting transaction fees. A good fee collection policy could considerably increase the chance of
delegates for being reelected in the next round, therefore they are incentivized to use creative and effective
methods\footnote{For example, they may
allow a limited number of free transactions per month for every account.}.

By the concept of request attachments, the Argennon protocol provides a method
for trust-less fee payment. When a user does not want to use off-chain fee payment methods, he can simply define his
transaction as the attachment
of the fee payment transaction. That way the fee payment transaction will be performed only if the attached
transaction is also included in the same block.

While transaction fee is not enforced by the Argennon protocol, there are other types of fee that are mandatory: the
\emph{database fee} and the \emph{block fee}. Both of these fees are required to be paid for every block of the Argennon
blockchain and are paid by the delegates. The block fee is a constant fee that is paid for each new block of the
blockchain and its amount is
determined by the ADAGs. The database fee depends on the data access and storage overhead that a new block
is imposing on the Argennon storage cloud. The amount of this fee is determined by the ADAGs, and is collected inside
a special account: the \texttt{dbFeeSink}.

@@

>>>>

The Argennon protocol does not explicitly define any fees for normal transactions. Only for high priority
transactions a fixed fee is determined by the governance system (See Section ...). Because the protection of the
Argennon network against spams and DOS attacks is mostly done by the delegates, they are also responsible for
determining and collecting transaction fees. A good fee collection policy could considerably increase the chance of
delegates for being reelected in the next terms, therefore they are incentivized to use creative and effective
methods\footnote{For example, they may
allow a limited number of free transactions per month for every account.}.

In Argennon fee payment can be done off-chain or on-chain. Off-chain fee payment is more efficient and flexible but
requires some level of trust in the delegates. For trust-less fee payment, the Argennon protocol provides the
concept of request attachments (See Section~\ref{sec:attachments}).
When a user does not want to use off-chain fee payment methods, he can simply define his transaction as the attachment
of the fee payment transaction. That way, the fee payment transaction will be performed only if the attached
transaction is also included in the same block.

While transaction fee is not enforced by the Argennon protocol, there are other types of fee that are mandatory: the
\emph{database fee} and the \emph{block fee}. Both of these fees are required to be paid for every block of the Argennon
blockchain and are paid by the delegates. The block fee is a constant fee that is paid for each new block of the
blockchain and its amount is
determined by the ADAGs. The database fee depends on the data access and storage overhead that a new block
is imposing on the Argennon storage cloud. The amount of this fee is determined by the ADAGs, and is collected in
a special account: the \texttt{dbFeeSink}.

@@

As long as ARG is allowed to be minted and its cap is not reached, the delegates will receive a reward at the
\textbf{end} of their election term. This reward will consist of newly minted ARGs, and its amount will be
determined by the ADAGs. In addition, for each block certificate that is added to the Argennon blockchain some amount
of ARGs will be minted and added to the \texttt{dbFeeSink} account.
